Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-01-28 Draft/description.tex
small typos fixed

\item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO} and of the general matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
The fast integration is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
The IR divergences appearing in the real corrections are handles with the help of the Cantani--Seymour dipole formalism \cite{Catani:1996vz,Dittmaier:1999mb}.
To numerically evaluate the one-loop scalar and tensor integrals, {\sc Recola} relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg}.
These tools have been successfully used for the computation of NLO corrections for high-multiplicity processes and in particlar VBS~\cite{Biedermann:2016yds,Biedermann:2017bss}.

>>>>

\item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO} and of the general matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
The fast integration is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
The IR divergences appearing in the real corrections are handles with the help of the Catani--Seymour dipole formalism \cite{Catani:1996vz,Dittmaier:1999mb}.
To numerically evaluate the one-loop scalar and tensor integrals, {\sc Recola} relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg}.
These tools have been successfully used for the computation of NLO corrections for high-multiplicity processes and in particular VBS~\cite{Biedermann:2016yds,Biedermann:2017bss}.
